GRB Afterglows In The Multi-Messenger Era

### 2018-07-10 structuredJets.tex
Added rough temporal slope figures.
adding in the flux equations for the different regimes into the appendix.

@@

>>>>

\section{Structured Phase}

\begin{figure}
	\plottwo{figs/slopesJet.png}{figs/slopesCocoon.png}
	\caption{Temporal slopes for the jet (left) and cocoon (right).}
\end{figure}

@@

The full flux scaling equations also require an updated energy and circumburst density scaling. For energy, it follows that (below $\nu_c$)
\begin{equation}
\frac{d \log F}{d \log E} = \frac{d \log F}{d \Psi} \frac{d \Psi}{d \log E} = - \frac{d \log F}{d \Psi} \frac{d \theta}{d \log E} = \left(s_1 - \frac{2}{3} s_2 - s_3 -\beta\right) h(\Psi) + 1 + \frac{1}{3} s_2,
\end{equation}
where
\begin{equation}
h(\Psi) \equiv \cot \Psi \frac{d \log E}{d \theta}.
\end{equation}
For the density $n_0$ we have (below $\nu_c$)
\begin{equation}
\frac{d \log F}{d \log n_0} = \frac{2+s_3}{8}
\end{equation}

Altogether, we obtain
\begin{eqnarray}
F_D & \propto & \epsilon_e^{-2/3} \epsilon_B^{1/3} n_0^{(2+s_3)/8} E^{\left(2/3 - s_3\right) h(\Psi) + 1} t_{obs}^{[-2+3s_3+3g(\Psi)]/[8+g(\Psi)]} \nu^{1/3} \nonumber \\
F_E & \propto & \epsilon_B^{1} n_0^{}
F_G & \propto & \epsilon_e^{p-1} \epsilon_B^{(1+p)/4} n_0^{(2+s_3)/8} E^{2ph(\Psi)+1} t_{obs}^{3[-2p+s_3+g(\Psi)]/[8+g(\Psi)]} \nu^{(1-p)/2} \nonumber \\
F_H & \propto & \epsilon_e^{p-1} \epsilon_B^{(p-2)/4} n_0^{(-2+s_3)/8} E^{(2p + 2/3 - s_3)h(\Psi) + 2/3} t_{obs}^{[-6p-2+3s_3+2g(\Psi)]/[8+g(\Psi)]} \nu^{-p/2}
\end{eqnarray}
